### 2023-04-13 output/group_0_crimes_warm_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.05 \\
 & Change in Crime Incidents, 2017-2019 & 0.00 & 0.93 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.02 & 0.63 \\
 & Job density, 2013 & 0.00 & 0.56 \\
 & Median household income, 2016 & 0.13 & 0.19 \\
 & Poverty rate, 2010 & 0.00 & 0.00 \\
 & Population density, 2010 & 0.00 & 0.14 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.71 & 0.01 \\
 & Filing without cause & 0.11 & 0.75 \\
 & Filing for nonpayment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.19 & 0.00 \\
 & Plaintiff has attorney & 0.70 & 0.07 \\
 & Defendant is entity & 0.00 & 0.04 \\
 & Plaintiff is entity & 0.19 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Crime Incidents, 2017 & 0.00 & 0.42 \\
 & Change in Crime Incidents, 2017-2019 & 0.00 & 0.26 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.88 \\
 & Job density, 2013 & 0.00 & 0.62 \\
 & Median household income, 2016 & 0.00 & 0.06 \\
 & Poverty rate, 2010 & 0.00 & 0.60 \\
 & Population density, 2010 & 0.00 & 0.38 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.11 & 0.01 \\
 & Filing without cause & 0.72 & 0.00 \\
 & Filing for nonpayment & 0.04 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.91 & 0.00 \\
 & Plaintiff has attorney & 0.53 & 0.00 \\
 & Defendant is entity & 0.31 & 0.00 \\
 & Plaintiff is entity & 0.01 & 0.02 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-13 output/group_1_crimes_500m/tables/balance_table.tex
placebo figure

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A}} & Total Group 1 Incidents, 2017 & 59.33 & 3.74 & 0.00 & 1.22 & 0.24 \\
 & $\Delta$ Group 1 Incidents, 2017-2019 & -14.54 & -0.44 & 0.45 & -0.35 & 0.56 \\
\cline{1-7}
\multirow[c]{3}{3cm}{\textit{Panel B}} & Job density, 2013 & 17,324.75 & 2,509.70 & 0.10 & 207.41 & 0.89 \\
 & Poverty rate, 2010 & 0.28 & -0.00 & 0.96 & 0.01 & 0.13 \\
 & Population density, 2010 & 23,285.59 & 1,452.05 & 0.00 & 479.29 & 0.27 \\
\cline{1-7}
\textit{Panel D} & Defendant is entity & 0.02 & -0.01 & 0.06 & 0.00 & 0.75 \\
\cline{1-7}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccccc}
\toprule
 &  & \textit{} & \multicolumn{4}{c}{\textit{Difference in Cases Won by Defendant}} \\
\cline{4-7}
\\
 &  & Cases Won by Plaintiff & Unweighted & \emph{p} & Weighted & \emph{p} \\
\midrule
\textit{Panel A} & Total Group 1 Incidents, 2017 & 81.75 & -2.95 & 0.50 & -2.42 & 0.58 \\
\cline{1-7}
\multirow[c]{5}{.75cm}{\textit{Panel B}} & Bachelor's degree, 2010 & 0.32 & 0.00 & 0.81 & -0.01 & 0.44 \\
 & Job density, 2013 & 16,161.03 & -1,272.66 & 0.55 & -535.86 & 0.80 \\
 & Median household income, 2016 & 47,553.06 & 2,997.87 & 0.01 & -1,006.45 & 0.32 \\
 & Poverty rate, 2010 & 0.28 & -0.02 & 0.00 & -0.01 & 0.21 \\
 & Population density, 2010 & 23,320.19 & -297.77 & 0.67 & -643.10 & 0.37 \\
\cline{1-7}
\textit{Panel C} & Filing for nonpayment & 0.72 & -0.11 & 0.00 & -0.03 & 0.08 \\
\cline{1-7}
\multirow[c]{2}{.75cm}{\textit{Panel D}} & Plaintiff has attorney & 0.88 & -0.05 & 0.00 & -0.03 & 0.05 \\
 & Plaintiff is entity & 0.81 & -0.08 & 0.00 & -0.03 & 0.08 \\
\cline{1-7}
\bottomrule
\end{tabular}

### 2023-04-13 output/group_1_crimes_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.80 \\
 & $\Delta$ Group 1 Incidents, 2017-2019 & 0.00 & 0.83 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.63 \\
 & Job density, 2013 & 0.00 & 0.70 \\
 & Median household income, 2016 & 0.00 & 0.03 \\
 & Poverty rate, 2010 & 0.00 & 0.00 \\
 & Population density, 2010 & 0.04 & 0.86 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.06 & 0.00 \\
 & Filing without cause & 0.48 & 0.03 \\
 & Filing for nonpayment & 0.85 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.37 & 0.00 \\
 & Plaintiff has attorney & 0.78 & 0.00 \\
 & Defendant is entity & 0.73 & 0.15 \\
 & Plaintiff is entity & 0.55 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 1 Incidents, 2017 & 0.00 & 0.50 \\
 & $\Delta$ Group 1 Incidents, 2017-2019 & 0.17 & 0.04 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.81 \\
 & Job density, 2013 & 0.00 & 0.55 \\
 & Median household income, 2016 & 0.00 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.00 \\
 & Population density, 2010 & 0.01 & 0.67 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.15 & 0.01 \\
 & Filing without cause & 0.46 & 0.03 \\
 & Filing for nonpayment & 0.02 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.15 & 0.00 \\
 & Plaintiff has attorney & 0.00 & 0.00 \\
 & Defendant is entity & 0.21 & 0.24 \\
 & Plaintiff is entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-13 output/group_2_crimes_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.78 \\
 & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.95 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.07 \\
 & Job density, 2013 & 0.00 & 0.15 \\
 & Median household income, 2016 & 0.00 & 0.03 \\
 & Poverty rate, 2010 & 0.00 & 0.00 \\
 & Population density, 2010 & 0.00 & 0.80 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.67 & 0.01 \\
 & Filing without cause & 0.89 & 0.59 \\
 & Filing for nonpayment & 0.61 & 0.02 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.88 & 0.04 \\
 & Plaintiff has attorney & 0.67 & 0.19 \\
 & Defendant is entity & 0.36 & 0.07 \\
 & Plaintiff is entity & 0.27 & 0.03 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 2 Incidents, 2017 & 0.00 & 0.92 \\
 & $\Delta$ Group 2 Incidents, 2017-2019 & 0.00 & 0.14 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.81 \\
 & Job density, 2013 & 0.00 & 0.55 \\
 & Median household income, 2016 & 0.00 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.00 \\
 & Population density, 2010 & 0.02 & 0.67 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.16 & 0.01 \\
 & Filing without cause & 0.67 & 0.03 \\
 & Filing for nonpayment & 0.01 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.91 & 0.00 \\
 & Plaintiff has attorney & 0.79 & 0.00 \\
 & Defendant is entity & 0.06 & 0.24 \\
 & Plaintiff is entity & 0.33 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-13 output/group_3_crimes_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 3 Incidents, 2017 & 0.00 & 0.16 \\
 & $\Delta$ Group 3 Incidents, 2017-2019 & 0.00 & 0.07 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.03 \\
 & Job density, 2013 & 0.00 & 0.29 \\
 & Median household income, 2016 & 0.00 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.01 \\
 & Population density, 2010 & 0.00 & 0.57 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.03 & 0.00 \\
 & Filing without cause & 0.02 & 0.16 \\
 & Filing for nonpayment & 0.00 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.27 & 0.00 \\
 & Plaintiff has attorney & 0.00 & 0.06 \\
 & Defendant is entity & 0.01 & 0.13 \\
 & Plaintiff is entity & 0.00 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 3 Incidents, 2017 & nan & nan \\
 & $\Delta$ Group 3 Incidents, 2017-2019 & nan & nan \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & nan & 0.81 \\
 & Job density, 2013 & nan & 0.55 \\
 & Median household income, 2016 & nan & 0.01 \\
 & Poverty rate, 2010 & nan & 0.00 \\
 & Population density, 2010 & nan & 0.67 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & nan & 0.01 \\
 & Filing without cause & nan & 0.03 \\
 & Filing for nonpayment & nan & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & nan & 0.00 \\
 & Plaintiff has attorney & nan & 0.00 \\
 & Defendant is entity & nan & 0.24 \\
 & Plaintiff is entity & nan & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-13 output/group_4_crimes_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 4 Incidents, 2017 & 0.00 & 0.56 \\
 & $\Delta$ Group 4 Incidents, 2017-2019 & 0.00 & 0.90 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.64 & 0.03 \\
 & Job density, 2013 & 0.00 & 0.29 \\
 & Median household income, 2016 & 0.54 & 0.01 \\
 & Poverty rate, 2010 & 0.25 & 0.01 \\
 & Population density, 2010 & 0.00 & 0.57 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.10 & 0.00 \\
 & Filing without cause & 0.28 & 0.16 \\
 & Filing for nonpayment & 0.07 & 0.04 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.31 & 0.00 \\
 & Plaintiff has attorney & 0.67 & 0.06 \\
 & Defendant is entity & 0.19 & 0.13 \\
 & Plaintiff is entity & 0.65 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 4 Incidents, 2017 & 0.00 & 0.23 \\
 & $\Delta$ Group 4 Incidents, 2017-2019 & 0.00 & 0.06 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.01 & 0.81 \\
 & Job density, 2013 & 0.38 & 0.55 \\
 & Median household income, 2016 & 0.00 & 0.01 \\
 & Poverty rate, 2010 & 0.05 & 0.00 \\
 & Population density, 2010 & 0.00 & 0.67 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.13 & 0.01 \\
 & Filing without cause & 0.66 & 0.03 \\
 & Filing for nonpayment & 0.16 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.49 & 0.00 \\
 & Plaintiff has attorney & 0.44 & 0.00 \\
 & Defendant is entity & 0.60 & 0.24 \\
 & Plaintiff is entity & 0.20 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

### 2023-04-13 output/group_5_crimes_500m/tables/pre_treatment_covariate_tests.tex
placebo figure

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  &  &  \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 5 Incidents, 2017 & nan & nan \\
 & $\Delta$ Group 5 Incidents, 2017-2019 & nan & nan \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & nan & 0.22 \\
 & Job density, 2013 & nan & 0.10 \\
 & Median household income, 2016 & nan & 0.05 \\
 & Poverty rate, 2010 & nan & 0.96 \\
 & Population density, 2010 & nan & 0.00 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & nan & 0.00 \\
 & Filing without cause & nan & 0.95 \\
 & Filing for nonpayment & nan & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & nan & 0.00 \\
 & Plaintiff has attorney & nan & 0.00 \\
 & Defendant is entity & nan & 0.06 \\
 & Plaintiff is entity & nan & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Dependent Variable}} \\
\cline{3-4}
\\
 &  & Change in Crime Incidents, April 2019-March 2020 & Treated Property \\
 & \emph{Independent Variable} &  &  \\
\midrule
\multirow[c]{2}{3cm}{\textit{Panel A: Pre-treatment Outcomes}} & Total Group 5 Incidents, 2017 & 0.00 & 0.25 \\
 & $\Delta$ Group 5 Incidents, 2017-2019 & 0.00 & 0.25 \\
\cline{1-4}
\multirow[c]{5}{3cm}{\textit{Panel B: Census Tract Characteristics}} & Bachelor's degree, 2010 & 0.00 & 0.81 \\
 & Job density, 2013 & 0.00 & 0.55 \\
 & Median household income, 2016 & 0.00 & 0.01 \\
 & Poverty rate, 2010 & 0.00 & 0.00 \\
 & Population density, 2010 & 0.41 & 0.67 \\
\cline{1-4}
\multirow[c]{3}{3cm}{\textit{Panel C: Case Initiation}} & Filing for cause & 0.59 & 0.01 \\
 & Filing without cause & 0.17 & 0.03 \\
 & Filing for nonpayment & 0.00 & 0.00 \\
\cline{1-4}
\multirow[c]{4}{3cm}{\textit{Panel D: Defendant and Plaintiff Characteristics}} & Defendant has attorney & 0.33 & 0.00 \\
 & Plaintiff has attorney & 0.75 & 0.00 \\
 & Defendant is entity & 0.00 & 0.24 \\
 & Plaintiff is entity & 0.90 & 0.00 \\
\cline{1-4}
\bottomrule
\end{tabular}
